\comboJob
{Chalmers}
{BSc course in Principle of Concurrent Programming}
{\MONTH{1} – \MONTH{3} 2023}
{Gothenburg, \SE}
{
\ifLong{%
% \cvline{
Teaching assistant (approx. 80 hours).
The course covered both shared-memory and message-passing
concurrency, using Java and Erlang as reference languages.
I provided assistance in lab sessions, grading of assignments and exams, and
Erlang coding tutorials.
%
% \cvlistitem{Concurrent systems. Communicating automata. Behavioural equivalences.}
% \cvlistitem{Real-time systems. Timed automata.}
% \cvlistitem{Process algebras: CCS, LNT.}
% \cvlistitem{Modal and temporal logics: HML, $\mu$-calculus, MCL. Model checking.}
% \cvlistitem{Model-based testing. Input-output conformance. Test case generation.}%
}
\ifShort{%
\begin{tightemize}
\item[] Shared-memory (Java) and message-passing (Erlang) concurrency
\item[] Approx. 80 hours of teaching assistance (lab sessions, grading, Erlang tutorial)
}
}

\comboJobZero
{Polytech Paris-Saclay}
{MSc course in Modelling and Verification}
{\MONTH{3} – \MONTH{4} 2022}
{Paris, \FR}
{}
\comboJob
{}
{}
{\MONTH{4} – \MONTH{5} 2021}
{}
{
\ifLong{%
% \cvline{
36-hour course for Master students in Computer Science Engineering,
\textit{filière apprentissage}.
Held remotely (2021) and in person (2022) as a supply teacher (\emph{intervenant vacataire}).
The course focused on the following topics:
modelling of concurrent systems through communicating automata (labelled
transition systems); behavioural equivalences; process algebras
(CCS, LNT); modal and temporal logics (HML, $\mu$-calculus, MCL);
model checking; modelling of real-time systems through timed automata;
model-based testing.
Tools such as CADP and UPPAAL were showcased in lab sessions.
%
%
% \cvlistitem{Concurrent systems. Communicating automata. Behavioural equivalences.}
% \cvlistitem{Real-time systems. Timed automata.}
% \cvlistitem{Process algebras: CCS, LNT.}
% \cvlistitem{Modal and temporal logics: HML, $\mu$-calculus, MCL. Model checking.}
% \cvlistitem{Model-based testing. Input-output conformance. Test case generation.}%
}
%
\ifShort{%
\begin{tightemize}
    \item[] 36-hour course for Master students in Computer Science Engineering
    (\textit{filière apprentissage}). Held remotely as a supply teacher (\emph{intervenant vacataire}).
    \item Concurrent, reactive, real-time systems. Communicating automata. Timed automata. 
    \item Behavioral equivalences of communicating automata.
    \item Process algebras: CCS, LNT. Modal and temporal logics: HML, $\mu$-calculus, MCL.
    \item Model-based testing. Input-output conformance. Test case generation.
    \item Lab sessions: 
    Uppaal (verification of timed automata);
    CADP (verification of concurrent systems);
    Testor (test case generation).
\end{tightemize}%
}
}

