\documentclass[11pt,a4paper]{moderncv}
\usepackage[T1]{fontenc}
\usepackage{microtype}
% \usepackage{times}
% \usepackage[top=5em, bottom=10em, hscale=0.63]{geometry}
\usepackage[a4paper, hscale=0.67]{geometry}
% \recomputelengths

\usepackage[bottom]{footmisc}

\moderncvstyle{banking}
\moderncvcolor{black}
\nopagenumbers{}

%% Comment this to remove references
% \newcommand*{\REFERENCES}{}

% Publications %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Set base style for biblatex-publist (do not use)
% \newcommand*\publistbasestyle{mla}

% Comment this to remove markers and other stuff related to highlighted publications
% \newcommand{\HIGHLIGHT}{}
\usepackage[%
    doi=false,bibstyle=publist,plnumbering=none,plauthorhandling=highlight,%
    hlyear=false,linktitles=doi,maxbibnames=99,citestyle=authoryear,
    giveninits=true,nameorder=given-family,uniquename=init
]{biblatex}
\ifx\HIGHLIGHT\undefined\else%
\renewbibmacro*{begentry}{%
\ifkeyword{highlight}{\makebox[0pt][r]{$\star$\addspace}}{}}
\fi
% \DefineBibliographyStrings{english}{%
%   toappear = {To appear},
% }

% \renewbibmacro*{begentry}{\ifkeyword{highlight}{\makebox[0pt][r]{$\star$\addspace}}{}}
% \plauthorname[Luca]{Di Stefano}
% \renewcommand*{\plauthorhl}[1]{#1}
\DeclareFieldInputHandler{extradate}{\def\NewValue{}}
\addbibresource{../publications.bib}
\defbibcheck{isjournal}{\ifentrytype{article}{}{\skipentry}}
\defbibcheck{isconference}{\ifentrytype{inproceedings}{}{\skipentry}}
\defbibcheck{ischapter}{\ifentrytype{inbook}{}{\skipentry}}
\defbibcheck{isreport}{\ifentrytype{report}{}{\ifkeyword{preprint}{}{\skipentry}}}
\defbibcheck{ismastersthesis}{\ifkeyword{mastersthesis}{}{\skipentry}}
\defbibheading{journals}{\subsection*{Journal articles}}
\defbibheading{conferences}{\subsection*{Peer-reviewed conference and workshop papers}}
\defbibheading{chapters}{\subsection*{Book chapters}}
\defbibheading{reports}{\subsection*{Preprints and technical reports}}
\defbibheading{masters}{\subsection*{Supervised Master's students}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{../commands.tex}

\author{Luca Di Stefano}
\date{\today}

\firstname{Luca}
\familyname{Di Stefano}
\extrainfo{Curriculum Vitae} 
\newdateformat{monthyear}{\monthname[\THEMONTH] \THEYEAR}
\quote{\normalfont \monthyear\today}
\usdate

\newcommand{\comboJob}[5]{%
\cventry{#3}{#2}{#1}{#4}{}{#5}%
}
\newcommand{\comboJobZero}[5]{%
\cventry[0pt]{#3}{#2}{#1}{#4}{}{#5}%
}

\newcommand*{\custombold}[1]{\textbf{#1}}
\newcommand*{\ifShort}[1]{}
\newcommand*{\ifLong}[1]{#1}


\newenvironment{tightemize}{\begin{itemize}\setlength\itemsep{0.2em}}{\end{itemize}}

\begin{document}

\makeatletter
\bfseries
\noindent {\Large\@author}\vspace*{0.4em}

\normalfont
\noindent {Curriculum vitae}

\noindent{\monthyear\today}
\makeatother

\section*{Personal information}
\begin{description}
    \item[E-mail:] \href{mailto:luca.di.stefano@tuwien.ac.at}{luca.di.stefano@tuwien.ac.at} 
    \item[Work address:] Treitlstraße 3, 1040, Vienna, Austria
    \item[Web page:] \url{https://www.lucadistefano.eu}
    \item[ORCID:] \url{https://orcid.org/0000-0003-1922-3151}
    \item[Scopus ID:] \href{https://www.scopus.com/authid/detail.uri?authorId=57205057932}{57205057932}
\end{description}

\section{Research interests}
My research mainly concerns the formal modelling and analysis of agent-based
models of complex collective systems.
On one hand, this entails the development of formally
defined high-level languages to concisely describe the features of individual
agents; on the other hand, it requires applying and improving state-of-the-art
verification techniques to check the collective behaviour of the resulting system.

Keywords associated with my interests include:

\cvline{Modelling}{%
Agent-based modelling,
Attribute-based communication,
Collective adaptive systems,
Domain-specific languages,
Multi-agent systems, 
Process algebras, 
Stigmergic interaction,
Structural operational semantics,
Temporal logics.
}

\cvline{Analysis}{%
Bounded model checking,
Explicit-state and symbolic model checking,
Software verification,
Static analysis.
}

\section*{Education}
\input{data/edu.tex}


\section*{Academic Career}
\input{data/jobs.tex}

\section*{Teaching}
\input{data/teaching.tex}

\printbibliography[heading=masters, check=ismastersthesis]

% \subsection*{Supervised students}
% \cvline{Master students}{%
% Love Lyckaro, Chalmers, 2023.
% \emph{Evaluating in-memory caching strategies for distributed Web services}.%
% }

\section*{Other academic activities}

\subsection{Reviewing activity}

\cvline{Conferences}{%
SEFM~2019,
TASE~2019,
%%%%%%%%%%%
AAMAS~2021,
FM~2021,
ICSOFT~2021,
ISoLA~2021,
%%%%%%%%%%%%
FORTE~2022,
ISoLA~2022,
%%%%%%%%%%%%
CSL~2023,
iFM~2023,
TACAS~2023,
%%%%%%%%%%%%
EMSOFT~2024,
FMICS~2024,
iFM~2024,
ISoLA~2024.
}

\cvline{Artifact evaluations}{%
COORDINATION~2023.
}

\cvline{Journals}{%
Logical Methods in Computer Science (2023),
Science of Computer Programming (2022, 2024),
Software Tools for Technology Transfer (2023, 2024).
}

\subsection*{Program Committees}
FMICS~2024, NSAD~2024, ASQAP~2025.

\subsection*{Workshop Chair}
FTfJP~2024.

% \vspace*{\itemsep}
% \cvlistitem{International Conference on Autonomous Agents and Multiagent Systems (AAMAS)}
% \cvlistitem{International Symposium on Formal Methods (FM)}
% \cvlistitem{International Conference on Formal Techniques for Distributed Objects, Components, and Systems (FORTE)}
% \cvlistitem{International Symposium On Leveraging Applications of Formal Methods, Verification and Validation (ISoLA)}
% \cvlistitem{International Conference on Software Technologies (ICSOFT)}
% \cvlistitem{Science of Computer Programming, Elsevier}
% \cvlistitem{International Conference on Software Engineering and Formal Methods (SEFM)}
% \cvlistitem{Theoretical Aspects of Software Engineering Conference (TASE)}

\subsection*{Participation to PhD schools}
\input{data/schools.tex}


\subsection*{Invited presentations}

\cvlistitem{\emph{Compositional Verification of Stigmergic Collective Systems.}
Invited presentation to the CONVECS research team (Inria/LIG).
Grenoble, France, 16 May 2023.
}

\cvlistitem{\emph{Verifying collective adaptive systems by emulation.}
Remote presentation to the Formal Methods unit of the Computer Science and
Engineering department (University of Gothenburg and Chalmers).
Gothenburg, Sweden, 10 March 2022.
}

\cvlistitem{\emph{Multi-agent (smart) systems with virtual stigmergies.}
Kickoff meeting of Italian national research project (PRIN)
\emph{IT MATTERS: Methods and Tools for Trustworthy Smart Systems.}
Pisa, Italy, 14 October 2019.
}
\cvlistitem{\emph{Multi-agent systems with virtual stigmergies.}
Invited presentation at IMT School for Advanced Studies.
Lucca, Italy, 3 July 2018.
}

\section*{Skills}
\cvline{Technical skills}{%
    My experience in programming spans more than a decade.
    As of now my languages of choice are mainly F\# and Python, but I have
    worked with a number of popular languages across the years
    (e.g., C, C++, C\#, Erlang, Go, Java, Prolog).
    I am familiar with software verification tools (CBMC, ESBMC, Infer),
    model checking software (CADP, NuXmv, SPIN),
    and SAT/SMT solvers (Glucose, MathSat, Minisat, Z3).
    I have some knowledge of control theory, computer architectures,
    assembly languages, and hardware description languages (mainly VHDL).
    I am also familiar with version control systems such as Git and
    Subversion.}
\vspace*{\itemsep}    
\cvline{Language skills}{
Italian is my first language.
I am fluent in English (CEFR level C1--C2)
and have some knowledge of French (CEFR level A2--B1).
I have basic Swedish skills (CEFR level A1).
}
% \cvline{Soft skills}{
% Having been the main contributor to multiple peer-reviewed scientific articles,
% I have acquired good academic writing skills, as well as an ability
% to work in groups, meet deadlines, and present my ideas both to my teammates
% and to external audiences.
% }

\section*{Publications}
\ifx\HIGHLIGHT\undefined\else%
Most relevant publications are highlighted by a $\star$.
\fi

\nocite{*}
\printbibliography[heading=journals, check=isjournal]
\printbibliography[heading=conferences, check=isconference]
\printbibliography[heading=chapters, check=ischapter]
\printbibliography[heading=reports, check=isreport]

\ifx\HIGHLIGHT\undefined\else%
\subsection*{Highlighted publications}
I was the main contributor to all the highlighted publications, except
(\cite{DBLP:journals/fmsd/StefanoL24}), where I mainly worked on the experimental
evaluation and on building a replication package to reproduce the results
presented in the article.
\fi

\subsection{Citation metrics}

As reported by Scopus on \today.

\cvline{}{} % For spacing
\cvline{Citations}{68}

\cvline{\emph{h}-index}{5}

% \section*{Received research grants}

% \cvlistitem{%
%     ``Verification of Emerging Properties in Collective Adaptive Systems''.
%     Short-term grant, December 2019 -- October 2020, IMT Lucca, Italy (see page~\pageref{grant:sysma}).}

    % \clearpage

\ifx\REFERENCES\undefined\else%
\section*{References}

For references, please contact: 

\vspace*{\itemsep}
\cvlistitem{%
    Rocco De Nicola,
    Professor of Computer Science,
    IMT School for Advanced Studies, Lucca, Italy.
    E-mail:~\href{mailto:rocco.denicola@imtlucca.it}{rocco.denicola@imtlucca.it}}
\cvlistitem{%
    Omar Inverso,
    Assistant Professor,
    Gran Sasso Science Institute, L'Aquila, Italy.
    E-mail:~\href{mailto:omar.inverso@gssi.it}{omar.inverso@gssi.it}}
% \cvlistitem{%
%     Frédéric Lang,
%     Research Fellow,
%     % Senior researcher,
%     Inria and LIG, Montbonnot Saint-Martin, Grenoble, France.
%     \mbox{E-mail:}~\href{mailto:frederic.lang@inria.fr}{frederic.lang@inria.fr}}

\cvlistitem{%
    Radu Mateescu,
    Research Director,
    % Senior researcher,
    Inria and LIG, Montbonnot Saint-Martin, Grenoble, France.
    \mbox{E-mail:}~\href{mailto:radu.mateescu@inria.fr}{radu.mateescu@inria.fr}}

\cvlistitem{%
    Nir Piterman,
    Full Professor,
    % Senior researcher,
    University of Gothenburg, Sweden.
    \mbox{E-mail:}~\href{mailto:piterman@chalmers.se}{piterman@chalmers.se}}

\vspace*{\itemsep}
Rocco De Nicola and Omar Inverso supervised my PhD thesis from 2017 to 2020.
% Frédéric Lang is a permanent member of the CONVECS research team
% (led by Radu Mateescu), where I worked as a post-doctoral researcher from 2020
% to 2022.
Radu Mateescu leads the CONVECS research team, where I worked as a post-doctoral researcher from 2020
to 2022.
Nir Piterman is the leader of my current research team in Gothenburg.
\fi

\end{document}
